Online {\IterComp}

### 2017-09-14 conclusions.tex
first attack on conclusions

\section{Conclusion and Future Work}

Our proposed technique for relaxed instrumentation can also be applied for similar profiling scenarios, such as profiling empirical computational complexity~\cite{goldsmith07,zaparanuks12,coppa14}.

>>>>

\section{Conclusions}
This paper has presented a novel work efficiency metric to enable one to compare the performance of any two different compiled versions of
a program without executing a given input more than once. This ability allows us to implement, for the first time, a true online iterative
compilation  to search for the best compilation options  based on actual user inputs seen in the deployment environment.

We develop a compiler-based, low-overhead instrumentation mechanism to gather the require data to evaluate the work metric. Our mechanism
does this without any human involvement. We show that by carefully selecting where to place the probes in the source code, the
instrumentation overhead can be negligible. We give two probe optimization strategies, allowing developers to balance the instrumentation
overhead and the performance error.

We  evaluate our approach using the KDataSets benchmark suit. Experimental results show that our approach delivers \red{80\%} of the
speedup achieved by an offline  oracle, but without executing any input more than once. We show that our probe optimization strategy is
highly effective, which brings the instrumentation overhead down to only \red{4\%} on average, making our approach practical for regular
use.

%Our proposed technique for relaxed instrumentation can also be applied for similar profiling scenarios, such as profiling empirical
%computational complexity~\cite{goldsmith07,zaparanuks12,coppa14}.

### 2017-09-14 motivation.tex
first attack on conclusions

Offline \itercomp can be very sensitive on having representative inputs for the program under optimization. If the developers cannot
predict what will be the typical usage of the application or that typical usage changes over time, then \itercomp might fail making the
application faster for the user.

@@

To show this, we performed offline \itercomp on \texttt{susan\_c} using a small subset of its inputs and we identified the optimization sequence that
maximizes performance. In Figure~\ref{fig:motivation-online}, the green bars are the histogram of speedups compared to \texttt{-O3} for
every individual input, while the dark green line shows the speedup averaged over all inputs. Despite the selected optimization sequence
being the best for some inputs, we see that on average it improves performance by only 6\% and hurts performance for almost half the
inputs. Just randomly choosing an input set for offline \itercomp can be counterproductive.

The blue bars in Figure~\ref{fig:motivation-online} show a different approach where during \itercomp the speedup of each optimization
sequence is again measured on a small input subset but this subset changes for every optimization sequence. This is similar to how online
\itercomp would have to work, using each input only once. This might introduce errors, since the speedups we measure for each optimization
sequence are not strictly comparable, they are measured on different workloads. But in the end the histogram shows that being able to test
more inputs allows us to make better informed decisions. The optimization sequence we selected never degrades performance compared to
\texttt{-O3} and is on average 13\% better than the offline approach.

\begin{figure}[t]
    \centering
    \includegraphics[width=0.5\textwidth]{figs/motivation-metric.pdf}
    \caption{Relationship between IPC and execution time vs optimization speedup for 500 different binaries of \texttt{susan\_c}. Each point represents
	averages over a distinct subsets of its inputs.}
    \label{fig:motivation-metric}
\end{figure}

@@

In the remaining of this paper, we examine our work efficiency metric, a novel way for approximating optimization speedup through a single
run which can be used to drive an online \itercomp methodology.

>>>>

The success of \itercomp relies on having representative inputs for the target program to be optimized. If the developers cannot predict
what will be the typical usage of the application or that typical usage changes over time, then \itercomp might fail making the application
faster for the user.

@@

To show this, we performed offline \itercomp on \texttt{susan\_c} from the \textit{KDataSets} benchmark suit~\cite{chen10,chen12a} using a
small subset of its inputs to identify the best-performing optimization sequence. In Figure~\ref{fig:motivation-online}, the green bars are
the histogram of speedups compared to \red{LLVM?} \texttt{-O3} for each individual input, while the dark green line shows the speedup
averaged over all inputs. Despite the selected optimization sequence being the best for some inputs, we see that it delivers, on average,
6\% of performance improvement, but gives slows down performance for nearly of the inputs. This example shows that randomly choosing an
input set to use for offline \itercomp can be counterproductive.

The blue bars \red{zw: the reviewer won't be able to see the difference if the paper is printed in black and white.} in
Figure~\ref{fig:motivation-online} show a different approach where during \itercomp the speedup of each optimization sequence is again
measured on a small input subset but this subset changes for every optimization sequence. This is similar to how online \itercomp would
have to work, using each input only once. This might introduce errors, since the speedups we measure for each optimization sequence are not
strictly comparable, they are measured on different workloads. But in the end the histogram shows that being able to test more inputs
allows us to make better informed decisions. The optimization sequence we selected never degrades performance compared to \texttt{-O3} and
is on average 13\% better than the offline approach.

\begin{figure}[t]
    \centering
    \includegraphics[width=0.5\textwidth]{figs/motivation-metric.pdf}
    \caption{Relationship between IPC and execution time vs optimization speedup for 500 different binaries of \texttt{susan\_c}. The binaries are compiled using different optimization sequences. Each point represents
	averages over a distinct subsets of its inputs.}
    \red{ZW: Perhaps take out the blue line (execution time). It is rather confusing. }
    \label{fig:motivation-metric}
\end{figure}

@@

In the remaining of this paper, we describe our work efficiency metric, which provides a new way for approximating optimization speedup
through a single run. We show that by utilizing this metric, a highly effective online \itercomp methodology can be built.
